---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(dialga)
```

# dialga

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done
yet, or the repository is only intended to be a limited example, demo,
or
proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
[![R-CMD-check](https://github.com/matt-dray/dialga/workflows/R-CMD-check/badge.svg)](https://github.com/matt-dray/dialga/actions)
[![Codecov test coverage](https://codecov.io/gh/matt-dray/dialga/branch/main/graph/badge.svg)](https://codecov.io/gh/matt-dray/dialga?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/matt-dray/dialga/badge)](https://www.codefactor.io/repository/github/matt-dray/dialga)
<!-- badges: end -->

## Purpose

{dialga} is an R package that helps you build and interpret standard [cron expressions](https://en.wikipedia.org/wiki/Cron#CRON_expression)---which are pretty esoteric---using friendly R syntax.

Under development. Just for fun. Bugs likely.

This package is a product of [Pokémon](https://www.pokemon.com/uk/)-Driven Development (PDD). Dialga is [the 'temporal Pokémon'](https://bulbapedia.bulbagarden.net/wiki/Dialga_(Pok%C3%A9mon)).

## Install

Install from GitHub with help from {remotes}:

```{r eval=FALSE}
install.packages("remotes")  # if not already installed
remotes::install_github("matt-dray/dialga")
library(dialga)
```

## Demonstration

There's currently two functions: `r2cron()` takes integer vectors as inputs to time-period arguments and spits out a cron string, and `cron2eng()` takes a valid cron string and prints out a readable English version. See `?dialga::r2cron()` and `?dialga::cron2eng()` for further details.

### Simple

A simple example of `r2cron()`: how would you specify the 28th minute past 11PM every day?

```{r r2cron-simple}
x <- dialga::r2cron(
  minutes = 28, 
  hours = 23,  # 24-hour clock
  clip = FALSE
)

x
```

To confirm, we can pass that cron string into `cron2eng()`. The output isn't sophisticated, but it communicates the point.

```{r cron2eng-simple}
dialga::cron2eng(x)
```

You could pipe these functions together to go from R to English.

```{r simple-pipe, message=FALSE}
library(magrittr)  # for %>%

dialga::r2cron(minutes = 28, hours = 23, clip = FALSE) %>% 
  dialga::cron2eng()
```

### Complex

A more complicated (i.e. contrived) request might be 'every 20 minutes from the zeroth minute of 3PM, 4PM and 5PM, on the 1st days of April, October and November, plus every weekend':

```{r r2cron-complex}
y <- dialga::r2cron(
 minutes = seq(0, 59, 20),
 hours = 15:17,  # 24-hr clock
 days_month = 1,
 months = c(4, 10, 11),
 days_week = c(1, 7),  # Sunday is '1'
 clip = FALSE
)

y
```

And in English:

```{r cron2eng-complex}
dialga::cron2eng(y)
```

### Warnings

As a courtesy, you'll be warned when unlikely dates arise:

```{r}
dialga::r2cron(days_month = 28:31, months = 2, clip = FALSE)
```

## Actual scheduling tools

If on Unix/Linux, you can use [the {cronR} package](https://github.com/bnosac/cronR) to schedule tasks from R. The Windows alternative is [the {taskscheduleR} package](https://github.com/bnosac/taskscheduleR). I typically use the web service [crontab.guru](https://crontab.guru) to build cron expressions. It was helpful for checking {dialga}'s functionality.

## Code of Conduct

Please note that the {dialga} project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
