---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(dialga)
```

# dialga

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done
yet, or the repository is only intended to be a limited example, demo,
or
proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
[![R-CMD-check](https://github.com/matt-dray/dialga/workflows/R-CMD-check/badge.svg)](https://github.com/matt-dray/dialga/actions)
[![Codecov test coverage](https://codecov.io/gh/matt-dray/dialga/branch/main/graph/badge.svg)](https://codecov.io/gh/matt-dray/dialga?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/matt-dray/dialga/badge)](https://www.codefactor.io/repository/github/matt-dray/dialga)
<!-- badges: end -->

Under development. Just for fun. Bugs likely.

## Purpose

{dialga} is an R package that (for now) helps you build standard [cron expressions](https://en.wikipedia.org/wiki/Cron#CRON_expression)---which are pretty esoteric---using friendly R syntax.

This package is a product of [Pokémon](https://www.pokemon.com/uk/)-Driven Development (PDD). Dialga is [the 'temporal Pokémon'](https://bulbapedia.bulbagarden.net/wiki/Dialga_(Pok%C3%A9mon)).

## Install

Install from GitHub with help from {remotes}:

```{r eval=FALSE}
install.packages("remotes")  # if not already installed
remotes::install_github("matt-dray/dialga")
library(dialga)
```

## Demonstration

Below are some demos of the `r2cron()` function. Arguments are named for each time period in a cron string (minutes, hours, etc) and their inputs can be in the form of:

* single integer values, like `1`
* consecutive-integer vectors, like `1:3`
* irregularly-spaced integer vectors, like `c(1, 2, 4)`
* regularly-spaced integer sequences, like `seq(3, 59, 15)` (useful for specifying sequences within the full time period, like 'every 15 minutes of the hour starting from minute 3' in this example)

See `?dialga::r2cron()` for further details.

The function defaults to 'every minute':

```{r r2cron-empty}
dialga::r2cron()
```

By default, the output will be printed and copied to your clipboard, thanks to [the {clipr} package](https://github.com/mdlincoln/clipr). Turn off copying with the argument `clip = FALSE`.

Here's 'every 15 minutes starting from the beginning of every hour':

```{r r2cron-15mins}
dialga::r2cron(minutes = seq(0, 59, 15), clip = FALSE)
```

A more complicated (i.e. contrived) request might be 'every 20 minutes from the zeroth minute of the hours 1500, 1600 and 1700, on the 1st day of April, October and November, plus every weekend':

```{r r2cron-complex}
dialga::r2cron(
 minutes = seq(0, 59, 20),
 hours = 15:17,  # 24-hr clock
 days_month = 1,
 months = c(4, 10, 11),
 days_week = c(1, 7),  # Sunday is '1'
 clip = FALSE
)
```

As a courtesy, you'll be warned when unlikely dates arise:

```{r}
dialga::r2cron(days_month = 28:31, months = 2, clip = FALSE)
```

## Actual scheduling tools

If on Unix/Linux, you can use [the {cronR} package](https://github.com/bnosac/cronR) to schedule tasks from R. The Windows alternative is [the {taskscheduleR} package](https://github.com/bnosac/taskscheduleR). I typically use the web service [crontab.guru](https://crontab.guru) to build cron expressions. It was helpful for checking {dialga}'s functionality.

## Code of Conduct

Please note that the {dialga} project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
